%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
%\fancyfoot[R]{\footnotesize Page \thepage\ of \pageref{LastPage}}
\fancyfoot[R]{Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

\header{Antony}{Wuth}{ } % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
100 Eucumbene Dr
Duffy, ACT, 2611
Australia
~
+61 (0) 414 254 157
+61 (02) 6287 4506
~
\href{mailto:ajw@pobox.com}{ajw@pobox.com}
\section{IT Administration}
Linux
Solaris
Oracle Database
Data Communications
TCP/IP Networking
ICT Metrics
Internet Services
DNS
HTTP
ICT Security
\section{ICT Design}
Gateway Environments
Network
Security
SOE
Web Applications
\section{ICT Audit}
Security
Firewall Review
Networks
Log Management and Review
\section{Languages}
Perl
Java
PHP
VGL
C
\section{IT Management}
Continuous Integration
Systems Monitoring
Network Monitoring
\end{aside}

%----------------------------------------------------------------------------------------
% BLAB-BY BIT
%----------------------------------------------------------------------------------------
\section{personal history}
I worked as a contracted theatrical technician as well as running a private help desk before becoming a contract programmer in February 1998. Over the next 5 years I worked with private enterprises, from small business through to the very large. Over the past 10 years I have worked in the Public Sector, enhancing and managing the Information Technology available to the Australian Government.

\subsubsection*{Staff Management}
Throughout my career I have been required to manage staff, a role I am comfortable in filling. Whilst at the Department of the Environment I was initially responsible for managing a small development team, and now manage a section of 16 IT professionals with a variety of skills.  I enjoy the interaction that comes with a management role and look forward to continuing this aspect of my career.  I particularly enjoy mentoring staff, it provides a significant personal satisfaction when I see staff excel.

\subsubsection*{Internet Technologies}
I have been involved in the Internet since 1991. I played a key role in the set up and operation of a small Internet Service Provider (ISP) CAPCOM. I currently administer a number of Internet sites in both Australia and overseas. I am involved with the Linux operating system, an Open Source system challenging the development practices of many traditional software developers. I have run Linux both privately and commercially since 1992. Over the past seven years I have been responsible for the management of secured internet gateway environments delivering secure, reliable and monitorable internet access to thousands of employees. These secured gateways host public facing web sites and applications listed as the most accessed Australian sites in their class.

\subsubsection*{ICT Security}
With the management of both internal and public facing systems comes a necessity to pro-actively manage a security posture. I have been actively involved in the security of IT systems for a number of organisations, including Government departments with International connections. In addition to the operational management of IT environments, I have prepared and interpreted policy documents, provided operational advice as well as participated in investigations. I regularly provide advice on how the changing policy environment will flow through to affect operational architecture and work practices.

\subsubsection*{Oracle \& Databases}
I have spent the last 15 years developing my Oracle and SQL skills. I have been responsible for the installation and configuration of new Oracle databases as well as ongoing adaptation to my clients requirements. I have become proficient in managing changes to database environments, while controlling the impact on planned objectives. While at the Australian Water Quality Center (AWQC) I was responsible for the planning and implementation of hardware environments to support a growing Data Warehouse providing the AWQC access to water testing results dating back to the early 1930’s. More recently I have led projects to upgrade to more recent releases of Oracle including re-engineering systems to take advantage of the new features available. I lead a project at the Department of the Environment to implement a virtualised environment for it's midrange and database systems a number of years before such implementations became a standard. This ground-breaking work led not only to significant financial savings but significant environmental efficiencies.

\subsubsection*{Web Development}
I have worked with a number of leading edge businesses in order to bring their products to the global Internet market. I have worked as a team leader to design, program and implement business critical software including e-commerce, financial and inventory management. A number of my clients have been purely online, requiring the utmost in software reliability. I have provided training in Internet technologies, both one-on-one, as well as in larger groups. Recently I have been assisting government clients with the development and deployment of Java based applications.

\subsubsection*{Budget Management}
Over the past five years I have been personally responsible for multi-million dollar budgets. I have been responsible for the management and delivery of large capital projects leading to significant improvements in the IT environment. While managing these budgets I frequently have to manage changing circumstances and demonstrate the diligence required with the expenditure of public money.

\subsubsection*{Personal Development}
I constantly strive to increase my knowledge, both through formal training and private study. I enjoy expanding my knowledge into new areas and am never satisfied in using a product or system without fully understanding the underlying technologies. I continue to expand my knowledge in the management and administration of information management technologies.


\pagebreak
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\vbox{%
\section{employment}
\begin{entrylist}
\entry
{2013-Present}
{Australian Government, Department of the Environment}
{Canberra, Australia}
{\emph{Director Platform Services Section} \\
Duties:
\begin{itemize}
\item Lead and manage a diverse team of ICT professionals
\item Financial management of multi-million dollar section budget including large multi-year ICT projects
\item Project management of both internal and externally delivered systems
\item Provide advice, participate and manage ICT procurement activities including large tender processes in the whole of government arena
\item Assist in new strategic initiatives both directly and via participation in steering committees and working groups
\item Manage external providers and consultants
\item Implement and manage mixed Linux and Windows servers
\item Participate in key audit processes including implementation of recommendations
\item Deliver key infrastructure projects:
\begin{itemize}
\item Migration to new Secured Intranet Gateway
\item Design and implementation of new metropolitan area network design
\item Implementation of the puppet configuration management system
\item Oracle Database and infrastructure upgrades
\end{itemize}
\end{itemize}}
%------------------------------------------------
\entry
{2008-2013}
{Australian Government, Department of Sustainability, Environment, Water, Population and Communities}
{Canberra, Australia}
{\emph{Director Environmental and Business Information Systems Section} \\
Duties:
\begin{itemize}
\item Lead and manage a diverse team of ICT professionals
\item Financial management of multi-million dollar section budget including large multi-year ICT projects
\item Project management of both internal and externally delivered systems
\item Assist in new strategic initiatives both directly and via participation in steering committees
\item Manage external providers and consultants
\item Implement and manage mixed Linux and Windows servers
\item Creation and implementation of resource management strategies (charge-back cost recovery)
\item Provide support for web based applications to both internal and external clients
\item Train and assist clients to effectively utilise information systems
\item Participate in a number of key initiatives including a tender process to source a new Departmental outsourcing provider
\item Participate in Whole of Government procurement and policy processes
\item Deliver key infrastructure projects:
\begin{itemize}
\item Oracle Database and infrastructure upgrades
\item Network security review, re-mediation and implementation
\end{itemize}
\end{itemize}}
\end{entrylist}}
\begin{entrylist}
%------------------------------------------------
\entry
{2004-2008}
{Australian Government, Department of Environment and Heritage}
{Canberra, Australia}
{\emph{Database and Internet Officer} \\
Duties:
\begin{itemize}
\item Develop, implement and manage Internet applications
\item Implement and manage mixed Unix (Solaris) and Windows servers
\item Provide support for web based applications to both internal and external clients
\item Manage relationships with external providers and consultants
\item Manage APS level staff
\item Train and assist clients to effectively utilise information systems
\end{itemize}}
%------------------------------------------------
\entry
{2002-2004}
{Cape3}
{Canberra, Australia}
{\emph{Senior Analyst - Web Programmer} \\
Duties:
\begin{itemize}
\item Design of back-end databases, including integration with legacy systems
\item Implementation of application designs in:
\begin{itemize}
\item ColdFusion
\item Perl
\item HTML
\item PHP
\end{itemize}
\item Assisting graphics designers to realise their vision
\item Design and specification of systems and network upgrades
\item Preparation of tender responses
\end{itemize}}
%------------------------------------------------
\entry
{1998-2002}
{Australian Water Quality Centre}
{Boliver, South Australia}
{\emph{Analyst / Programmer} \\
Duties:
\begin{itemize}
\item Power Builder development
\item Development of database reporting software
\item Migration and cleansing of data from legacy systems
\item Interfacing financial and laboratory systems
\item Design and implementation of work scheduling systems
\item Providing support for the Sample Manager laboratory management system
\item Maintenance and improvement of Laboratory Information systems
\item VGL Programming
\item UNIX Administration
\item Support for AIX 4.x on RS/6000 hardware
\item Planning and supervision of systems upgrades
\item Administration and Maintenance of Oracle 7.3, 8 \& 9i systems
\item Year 2000 (Y2K) systems testing and re-mediation
\item Testing of complex integrated applications over multiple environments
\item Liaison with external suppliers
\end{itemize}}
%------------------------------------------------
\entry
{1993-1997}
{Freelance PC / Network Technical Support}
{Canberra, ACT}
{\emph{Analyst / Programmer} \\
Duties:
\begin{itemize}
\item Procurement of hardware and software
\item Network installation and troubleshooting
\item Hardware upgrades and maintenance
\item Remote Help Desk support to clients
\item Internet training
\end{itemize}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\vbox{%
\section{awards}
\begin{entrylist}
\entry
{2013}
{Australia Day Award}
{Australian Government, Department of Sustainability, Environment, Water, Population and Communities}
{Awarded for sustained contribution to redevelopment of the Department's web presence, including re-engineering of the web hosting platform}
%------------------------------------------------
\entry
{2009}
{Secretary's Award}
{Department of the Environment, Water, Heritage and the Arts}
{Awarded for sustained contribution towards realising the Department's outcomes}
%------------------------------------------------
\entry
{2007}
{Division Head's Award}
{Corporate Strategies Division, Department of the Environment}
{Awarded for excellent management of the Department's mid-range database, infrastructure and web information systems}
%------------------------------------------------
\entry
{2007}
{Division Head's Award}
{Corporate Strategies Division, Department of the Environment}
{Awarded for excellent support to the Department's web information systems}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{communication skills}

\begin{entrylist}
%------------------------------------------------
\entry
{2013}
{Oral Presentation}
{Splunk live}
{Presented the Department's implementation of Splunk as a security and log management system.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}
\begin{entrylist}
%------------------------------------------------
\entry
{2012}
{Splunk, search administration, installation}
{ }
{ }
%------------------------------------------------
\entry
{2011}
{Project Management Best Practice}
{Dept. of Environment and Heritage}
{ }
%------------------------------------------------
\entry
{2004-present}
{Oracle {\normalfont Database Administration and feature updates}}
{Oracle Corporation}
{ }
%------------------------------------------------
\entry
{1999}
{Oracle {\normalfont Database Administration}}
{Oracle Corporation, Canberra}
{ }
%------------------------------------------------
\entry
{1999}
{Sample Manager {\normalfont Administration}}
{LabSystems Australia, Adelaide}
{ }
%------------------------------------------------
\entry
{1998}
{Sample Manager {\normalfont Advanced VGL Programming}}
{LabSystems Australia, Sydney}
{ }
%------------------------------------------------
\entry
{1997}
{Diploma {\normalfont Diploma of Business Programming}}
{CPTI, Canberra}
{C, COBOL, Visual Basic, SQL, business applications, operating systems and network operating systems}
%------------------------------------------------
\entry
{1993}
{Year 12 Certificate}
{St Edmunds College, Canberra}
{ }
\end{entrylist}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} ICT \& physical security, solution design, systems automation, process quality improvement.

\textbf{personal:} Cycling, fish-keeping, home-automation, cooking, electronics, embedded programming, wood working.

%----------------------------------------------------------------------------------------
} %End last page vbox
\end{document}
